---
title: "section1C_stream_reach_physical_char"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "4/16/2020"
output:
  word_document: default
---

 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)

#set up the file path
file.path.h=file.path(here::here(),
          "data",
          "habitat_wk.csv")

file.path.s<-file.path(here::here(),
                       "data",
                       "sites_wallkill_sturg.csv")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
#function to make the sites a factor in order from upstream to downstream
order_sites<-function(df, sites_table, df_site_col, sites_site_col){
Sites<-sites_table%>%
  dplyr::rename(SITE_ID=sites_site_col)

df<-df%>%
  dplyr::rename(SITE_ID=df_site_col)

all_data<-left_join(df, Sites)
all_data<-all_data%>%
  dplyr::arrange(order)%>%
  dplyr::mutate(SITE_ID=factor(SITE_ID, levels = unique(SITE_ID)))

columns<-colnames(Sites)
columns<-columns[!(columns %in% "SITE_ID")]

all_data<-all_data%>%
  dplyr::select(!tidyselect::any_of(columns))
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#read in the habitat data
habit<-read.csv(file.path.h,stringsAsFactors = FALSE)

#select relevant columns
habit<-habit %>% 
  select("Location ID" =SITE_ID, "Collection \n Date"=COLL_DATE, "Gradient"=HFDH_GRADIENT, "Epi.\n Cover"=HFDH_EPIFAUNAL_COVER, "Embed. \n Pool."=HFDH_EMBEDDEDNESS_POOLING, "Vel/Dep. \n Reg"=HFDH_VELOCITY_DEPTH_REGIME,
         "Sed. \n Dep."=HFDH_SEDIMENT_DEPOSITION, "Flow \n Status"=HFDH_FLOW_STATUS, "Chan. \n Alt"=HFDH_CHANNEL_ALTERATION, "Rif. \n Freq"=HFDH_RIFFLE_BEND_FREQUENCY, "L.B. \n Stability"=HFDH_LEFT_BANK_STABILITY, "R.B. \n Stability"= HFDH_RIGHT_BANK_STABILITY, "L.B. \n Veg"= HFDH_LEFT_BANK_VEG, "R.B.\n Veg"=HFDH_RIGHT_BANK_VEG, "L.B. \n Veg Zone"=HFDH_LEFT_BANK_VEG_ZONE, "R.B. \n Veg Zone"=HFDH_RIGHT_BANK_VEG_ZONE) 

library(lubridate)
habit<-habit %>% 
  mutate(year=year(`Collection \n Date`))

#limit to last 3 years

habit<-habit %>% 
  filter(year >= 2017)

#read in sites table and reorder sites upstream to downstream
sites<-read.csv(file.path.s,stringsAsFactors = FALSE)

habit<-habit%>%
  order_sites(sites_table = sites, df_site_col = "Location ID", sites_site_col = "SH_SITE_ID")

habit$year<-NULL
#get pwl into the figure
pwl<-sites %>% 
  select(SH_PWL_ID,SH_SITE_ID,order) %>% 
  rename(SITE_ID=SH_SITE_ID)

#Average all entries per site
habit<-habit%>%
  group_by(SITE_ID, Gradient)%>%
  summarize(`Epi.\n Cover`=mean(`Epi.\n Cover`),
            `Embed. \n Pool.`=mean(`Embed. \n Pool.`),
            `Vel/Dep. \n Reg.`=mean(`Vel/Dep. \n Reg`),
            `Sed. \n Dep.`=mean(`Sed. \n Dep.`),
            `Flow \n Status`=mean(`Flow \n Status`),
            `Chan. \n Alt`=mean(`Chan. \n Alt`),
            `Rif. \n Freq`=mean(`Rif. \n Freq`),
            `L.B. \n Stability`=mean(`L.B. \n Stability`),
            `R.B. \n Stability`=mean(`R.B. \n Stability`),
            `L.B. \n Veg`=mean(`L.B. \n Veg`),
            `R.B.\n Veg`=mean(`R.B.\n Veg`),
            `L.B. \n Veg Zone`=mean(`L.B. \n Veg Zone`),
            `R.B. \n Veg Zone`=mean(`R.B. \n Veg Zone`))

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Add HMA model values to the table, add columns to see whether the model or stream score is lower, calculate HMA, add column to interpret HMA score
habit.hma<-habit%>%
  mutate(EpiCoverM=case_when(
    Gradient=="High" ~ 17,
    TRUE ~ 14),
    EmbedM=case_when(
      Gradient=="High" ~ 17,
      TRUE ~ 13),
    VelDepM=case_when(
      Gradient=="High" ~ 19,
      TRUE~10),
    SedDepM=case_when(
      Gradient=="High" ~ 18,
      TRUE ~ 14),
    FlowM=case_when(
      Gradient=="High" ~19,
      TRUE ~17),
    ChanM=case_when(
      Gradient=="High"~ 18,
      TRUE ~ 17),
    RiffleM=case_when(
      Gradient=="High"~ 19,
      TRUE~ 14),
    StabilityM=18,
    VegM=case_when(
      Gradient=="High" ~ 18,
      TRUE ~ 17),
    VegZoneM=case_when(
      Gradient=="High" ~ 18,
      TRUE ~ 15),
    EpiCover.Low= case_when(
      `Epi.
 Cover`<= EpiCoverM ~ `Epi.
 Cover`,
 TRUE ~ EpiCoverM),
  Embed.Low=case_when(
    `Embed. 
 Pool.`<=EmbedM ~ `Embed. 
 Pool.`,
 TRUE~EmbedM),
 VelDep.Low=case_when(
   `Vel/Dep. 
 Reg.`<=VelDepM ~ `Vel/Dep. 
 Reg.`,
 TRUE~ VelDepM),
 SedDep.Low=case_when(
   `Sed. 
 Dep.`<=SedDepM ~ `Sed. 
 Dep.`,
 TRUE~ SedDepM),
 Flow.Low=case_when(
   `Flow 
 Status`<=FlowM ~ `Flow 
 Status`,
 TRUE ~ FlowM),
 Chan.Low=case_when(
   `Chan. 
 Alt`<=ChanM ~ `Chan. 
 Alt`,
 TRUE~ ChanM),
 Riffle.Low=case_when(
   `Rif. 
 Freq`<=RiffleM ~ `Rif. 
 Freq`,
 TRUE ~ RiffleM),
 Stability.Low=case_when(
   (`L.B. \n Stability`+ `R.B. \n Stability`)<=StabilityM ~ (`L.B. \n Stability`+ `R.B. \n Stability`),
   TRUE~ StabilityM),
 Veg.Low=case_when(
   (`L.B. \n Veg`+`R.B.\n Veg`)<=VegM ~ (`L.B. \n Veg`+`R.B.\n Veg`),
   TRUE ~ VegM),
 Veg.Zone.Low=case_when(
   (`L.B. \n Veg Zone`+ `R.B. \n Veg Zone`)<= VegZoneM ~ (`L.B. \n Veg Zone`+ `R.B. \n Veg Zone`),
   TRUE~VegZoneM),
 `HMA \n Score`= case_when(
   Gradient=="High" ~(EpiCover.Low+ Embed.Low+ VelDep.Low+ SedDep.Low+ Flow.Low+ Chan.Low+ Riffle.Low+ Stability.Low+Veg.Low+ Veg.Zone.Low)/181*100,
   TRUE ~ (EpiCover.Low+ Embed.Low+ VelDep.Low+ SedDep.Low+ Flow.Low+ Chan.Low+ Riffle.Low+ Stability.Low+Veg.Low+ Veg.Zone.Low)/149*100),
 `HMA \n Assess.`=case_when(
   `HMA \n Score`>=80 ~ "Natural",
   `HMA \n Score`>=70&`HMA \n Score`<80 ~ "Altered",
   `HMA \n Score`>=60 & `HMA \n Score` <70 ~ "Moderate",
   TRUE~ "Severe"
 ))


habit.hma$`HMA \n Score`<-round(habit.hma$`HMA 
 Score`, 1)

HMA_counts<-habit.hma%>%
  rename(Assessment=`HMA 
 Assess.`)
```


Assessments of physical habitat conditions were performed by field crews at sites along with macroinvertebrate collections following the methods detailed in section 9.10 of SOP #208-19. Each habitat category was averaged over the two years of sampling conducted at each location. The information collected in these assessments are used to calculate the Habitat Model Affinity (HMA) (Table 3), an overall estimate of habitat quality which describes potential habitat stress on aquatic life. The HMA is based on rankings of individual habitat characteristics on a scale from 0 (poor) to 20 (optimal) which are then compared to a statewide reference condition (Appendix IV). HMA scores are used to make final physical habitat assessments; Natural (80-100), Altered (70 – 80), Moderate (60 – 70), and Severe (< 60). Results are described in terms of percent similarity to the reference condition. 

Habitat model affinity (HMA) scores and resulting final physical habitat assessments ranged from natural to severe alteration across all sites (SOP #208-19; Table\@ref(tab:Habitat-table)). Physical habitat final assessments demonstrate that habitat may have been a factor influencing benthic communities at sampling locations where HMA scores indicate moderate or severely altered conditions (Table\@ref(tab:Habitat-table)); natural (n=`r sum(HMA_counts$Assessment=="Natural")`), altered (n=`r sum(HMA_counts$Assessment=="Altered")`), moderate (n=`r sum(HMA_counts$Assessment=="Moderate")`), severe (n=`r sum(HMA_counts$Assessment=="Severe")`).


<!---BLOCK_LANDSCAPE_START--->

```{r tab.id="Habitat-table", tab.cap="Ranked habitat characteristics and calculated HMA for the Wallkill River Survey, 2017-2019. Epifaunal substrate (Epi. Cover); Embeddedness/Pool Substrate Characterization (Embed. Pool.); Velocity Depth Regime/Pool Variability (Vel/Dep Reg.); Sediment Deposition (Sed. Dep.); Channel Flow Status (Flow Status); Channel Alteration (Chan. Alt.); Riffle Frequency/Stream Sinuosity (Rif. Freq.); Left and Right Bank Stability (L.B. and R.B. Stability); Left and Right Bank Vegetation (L.B. and R.B. Veg); Width of Left and Right Bank Vegetative Zone (L.B. and R.B. Veg Zone); Habitat Model Affinity Score (HMA Score); HMA Assessment (HMA Assess.)", echo=FALSE, message=FALSE,warning=FALSE}
#table
#get pwl into the table

habit.hma<-merge(habit.hma, pwl, by="SITE_ID")

habit.hma<-habit.hma %>% 
  arrange(order)
habit.hma$order<-NULL

habit.hma<-habit.hma %>% 
  rename("PWL ID"=SH_PWL_ID)

#create function for common tables
#df is the data frame, x and y are the column numbers you want centered, z is the caption
table.f<-function(df,x,y){
 library(flextable)
  tl<-flextable(df) %>% font(i = NULL, j = NULL, fontname="Arial", part = "all")
tl<-align(tl, i = NULL, j =(x:y) , align = "center", part = "all")
tl
}

#call the function
tl<-table.f(habit.hma[,c(38,1,2:15,36,37)],2,17)

#this part might have to be figured out later, with a larger caption/table function? Not sure yet.



tl<-tl%>%
  fontsize(size=10, part = "all")%>%
  #width(j=1:18, width=0.4)%>%
  #width(j=c(4,5,10,11), width = 0.5)%>%
  #width(j=c(17), width=0.6)%>%
  #width(j=1, width=0.8) %>% 
  fit_to_width(max_width = 10.5) %>% 
  flextable::merge_v(j=c("PWL ID")) %>% 
  fix_border_issues() %>% 
  theme_zebra() %>% 
  flextable::bg(j=1,part = "body",bg = "white") %>% 
  flextable::border(part = "body",border.bottom = officer::fp_border(color="grey")) %>% 
  flextable::border(part = "body",j=1,border.right = officer::fp_border(color = "grey"))
  

tl

```

<!---BLOCK_LANDSCAPE_STOP--->


```{r echo=FALSE, message=FALSE,warning=FALSE}
HMA_counts<-habit.hma%>%
  rename(Assessment=`HMA 
 Assess.`)
```

